Estimating contemporary migration numbers of adults for iteroparous species using kinship pairs found between populations

### 2022-02-03 latex/ms.tex
write 3rd more para in Intro, #15

There are essentially two approaches for estimating the contemporary migration rate. The first is to use the mark-recapture (MR) method that directly estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}. The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval. While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate (REF). In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.

 \RED{KOKOMADE}

@@

% 4: CKMR can cover the range that Mark recapture can handle with more realistic situations
% 5: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
% 6: In this paper, ~

There are essentially two approaches for estimating the migrant number. The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data. The second is to ...

@@

%PRE-DEFINED population !
%Caveat: selectivity, family correlated migration、skip spawning,

>>>>

There are essentially two approaches for estimating the contemporary migration rate. The first is to use the mark-recapture (MR) method that estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}. The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval. While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate (REF). In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.

@@

The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{Pritchard_2000}. The model of \cite{Wilson_2003}, which is one of such population assignment (PA) methods and implemented in a software BayesAss, can output the point estimate as an element of a current migration matrix. However, as evaluated by several authors \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of estimated migration rates by the model is valid only when populations are highly differentiated ($F_{\rm ST}\ge0.05$), suggesting that it may be difficult to infer the degree of demographic dependency among populations since demographic independency is realized even if there are many migrants.

% 4: CKMR can cover the range that Mark recapture can handle with more realistic situations

Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[]{https://doi.org/10.1111/faf.12615}.

This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}. Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$. While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}. This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.

% 5: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
% 6: In this paper, ~

@@

%  (e.g., \cite{Hastings_1993} numerically demonstrates that two populations become demographically independent when migration rate $< 0.1$)
% withinのデータはどう使う？？
%PRE-DEFINED population !
%Caveat: selectivity, family correlated migration、skip spawning,
